### 2018-11-30 tex/paper.tex
New section: higher-order Potts model described and LP relaxation specified.

>>>>

\mysection{Higher-order Potts Model} The pairwise Potts model often fails
to capture useful image statistics because it restricts the order of the
potentials to be at most two. Higher order clique potentials can model complex
interactions of random variables, and thereby overcome this difficulty.

The simplest generalisation of pairwise Potts model to higher-order results in
\textit{higher-order Potts model}. The clique potentials for these models are
defined as

\begin{equation}
  \phi_c({\bf x}_c) = 
  \begin{cases}
    \gamma_0, &{\text{if}} \; \forall i, j \in c: x_i = x_j, \\
    \gamma_1, &{\text{else}}. 
  \end{cases} 
\end{equation}

\myparagraph{LP Relaxation}
\begin{align}
    \text{(HOP-LP)} \quad \min_{\bf y} \enskip & E({\bf y}) =  \sum_{a = 1}^N
    \sum_{i = 1}^L \phi_a(i)y_{ai} + \nonumber\\
    &\sum_{c \in {\mathcal C}} \max_{(a, b) \in c} \frac{w_c}{2} \sum_{i = 1}^L \cdot |y_{ai} - y_{bi}| \nonumber\\
    \text{s.t} \quad &{\bf y} \in \Delta.
\label{eq:hop-lp}
\end{align}
The constraints for (HOP-LP) are the same as for (P-LP).
